### 2018-02-10 results.Rnw
work on #1

fig3 <- cowplot::plot_grid(
                          legend,
                          fig3A +  my_theme,
                          fig3B +  my_theme,
                          nrow=1,
                          labels=c("", "A", "B"),
                          rel_widths = c(1, 2, 2),
                          label_size = 20,
                          axis="b",
                          align="h"
                          )
pdf("../fig/fig-3.pdf",w=10,h=10)
print(fig3)
tmp  <- dev.off()

@@

figS1 <- cowplot::plot_grid(
                          figS1A,
                          figS1B,
                          nrow=1,
                          labels=c( "A", "B"),
                          label_size = 20,
                          align="v"
                          )

@@

fig4 <- cowplot::plot_grid(
				fig4A,
				fig4B,
				nrow=1,
				labels=c("A", "B"),
				align="v"
)

pdf("../fig/fig-4.pdf",w=10,h=3)
print(fig4)
tmp  <- dev.off()

@@

fig5 <- cowplot::plot_grid(fig5A + theme(legend.position="none"),
                           fig5B + theme(legend.position="bottom"),
                           fig5C + theme(legend.position="none"),
                           nrow=1,
                           label_size = 20,
                           align = "hv",
                           axis="b",
                           labels=c( "A", "B", "C")
                           #?cowplot::plot_grid
                           )
pdf("../fig/fig-5.pdf",w=10,h=5)
print(fig5)
tmp <- dev.off()
@

>>>>

fig3 <- cowplot::plot_grid(
                          legend,
                          fig3A +  my_theme,
                          fig3B +  my_theme,
                          nrow=1,
                          labels=c("A", "", "B"),
                          rel_widths = c(1, 2, 2),
                          label_size = 32,
                          axis="b",
                          align="h",
                          hjust=0, vjust=1.01
                          )
pdf("../fig/fig-3.pdf",w=12,h=12)
print(fig3)
tmp  <- dev.off()

@@

figS1 <- cowplot::plot_grid(
                          figS1A,
                          figS1B,
                          nrow=1,
                          labels=c( "A", "B"),
                          label_size = 32,
                          align="v",
                          axis="b",
                          hjust=0, vjust=1.01
                          )

@@

fig4 <- cowplot::plot_grid(
				fig4A,
				fig4B,
				nrow=1,
				labels=c("A", "B"),
				align="v",
				axis="b",
				label_size = 32,
				hjust=0, vjust=1.01
)

pdf("../fig/fig-4.pdf",w=12,h=4)
print(fig4)
tmp  <- dev.off()

@@

fig5 <- cowplot::plot_grid(fig5A + theme(legend.position="none"),
                           fig5B + theme(legend.position="bottom"),
                           fig5C + theme(legend.position="none"),
                           nrow=1,
                           label_size = 32,
                           align = "hv",
                           axis="b",
                           labels=c( "A", "B", "C"),
                           hjust=0, vjust=1.01
                           #?cowplot::plot_grid
                           )
pdf("../fig/fig-5.pdf",w=12,h=6)
print(fig5)
tmp <- dev.off()
@
